Effects of CHILDREN's programs

### 2020-02-26 paper.tex
ghjhj

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 14:56:01 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

At the beginning of the time series in 2011, in the Lunch program they supported in 52 organizations. In 2018, this number has increased to 68. In 2011, CHILDREN financed meals for 3748 beneficiaries, and for 5103 in 2018. In the trips program, which launched in 2012, the number of supported organizations amounted to 44 in 2012 and grew to 49 until 2018. In 2012, their grant allowed 2803 beneficiaries to go on trips, and 6911 in 2018. In this section, we give an overview of the dynamics of CHILDREN's two flagship programs. We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary. We also look at selected outcomes, i.e. those related to health as well as self-worth and day-to-day skills. We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt). We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur). These are only available after logging in on DESTATIS. The organizations also gave information about their total yearly budget. We inflate this with the general price index.

@@

\floatfoot{This graph shows the development of grants in the Meals compared to the Trips program. We distinguish between the sum of grants in one year, the median and the median grant per beneficiary. From left to right: Meals, Trips, from top to bottom: sum, median, median per beneficiary. We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
\end{figure}

For the dynamics of figure 2 we have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt). We distinguish between the sum of grants in one year, the median and the median grant per beneficiary and between the Lunch and Trips Program.

Figure 2 shows no exact trend for the total real grant for the Lunch program. Between 2013 and 2015 the grant increased from about 600000 EUR to 680000 EUR, but falls behind in the following year. Since 2017, an increase is again visible. In comparison to this, there is a clearer negative trend in median Meals subsidy, falling from about 8000 EUR in 2012 to about 6500 EUR in 2018. In accordance, the median Meals grant per beneficiary shrinks from about 250 EUR to about 200 EUR.

In the total Trips grant, a slightly negative trend is visible, after the subsidy increased to approximately 200000 EUR in 2014, but decreased to about 130000 EUR in 2016, and is connstand eversince. The Trips median grant therefore also decreased from 3000 EUR to 2000 EUR over the time period, as well as the median grant per beneficiary decreased from about 60 EUR to about 30 EUR.
These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table 1, that children was able to increase the number of organizations they support, but had to distribute the available subsidy among them.

@@

@@

\begin{equation}
\label{Equation 1}
  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
\end{equation}

In this section we use a standard OLS equation, as described in equation 1. Where needed, we modified the given data, by using weights, excluding outliers and by scaling relevant variables. We also compared the results with the actual dataset to the results we gained by using a dataset in which we imputed necessary data. (DESCRIBE METHODS EXACT)

\subsection{Variables of interest: Number of trips and number of meals}

As the first variables of interest we consider the number of meals the organizations recorded and the number of trips the organizations made together with the beneficiaries. In this case, we use standard OLS in a first equation, exclude outliers from the variables 'mealsNo' and 'tripsNo' to obtain a believable value and compare to the imputed dataset. TableX shows the regression results.

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
\hline
R$^2$       & 0.43            & 0.13            & 0.45             \\
Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
Num. obs.   & 329             & 250             & 440              \\
RMSE        & 39992.79        & 3629.72         & 39601.41         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of meals}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept)      & $3.70^{***}$ & $2.62^{***}$ & $3.62^{***}$ \\
                 & $(0.33)$     & $(0.23)$     & $(0.33)$     \\
realTripsSubsidy & $0.00^{*}$   & $0.00^{***}$ & $0.00^{*}$   \\
                 & $(0.00)$     & $(0.00)$     & $(0.00)$     \\
\hline
R$^2$            & 0.05         & 0.09         & 0.05         \\
Adj. R$^2$       & 0.04         & 0.08         & 0.05         \\
Num. obs.        & 322          & 257          & 334          \\
RMSE             & 2.96         & 1.70         & 2.93         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of trips}
\label{table:coefficients}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
\hline
R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
Num. obs.           & 121          & 120         & 177          & 177          \\
RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Less Ill}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
\hline
R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
Num. obs.           & 214      & 212      & 275        & 275      \\
RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Dietary Knowledge}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
\hline
R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
Num. obs.           & 213          & 211      & 274          & 274        \\
RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Appreciate Healthy}
\label{table:coefficients}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
Num. obs.                      & 428      & 184      & 430      & 187      \\
RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Selfworth}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
Num. obs.                      & 426      & 177      & 429      & 181      \\
RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: dayToDaySkills}
\label{table:coefficients}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 14:56:06
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

Outliers?

>>>>

Many organizations do not answer all questions CHILDREN poses. We create a seperate data set, in which we impute missing values with an organization-specific linear trend. CHILDREN supports some very large organizations that give out hundreds of meals a day or conduct dozens of trips per year. We fit our models with outliers excluded to see if they are driving results. We define an outlier as a value that is at least 1.5 interquartile ranges below the 25th percentile or equally far above the 75th percentile. Once we exclude outliers in terms of numbers of meals and once in terms of number of trips.

\begin{figure}
  \caption{Trend in everyday expertise and selfworth}
  \label{LineDisp}

{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-2-1}

\floatfoot{The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012. The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y). The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line. Additionally, the linear trends of both groups are included as the straight lines.}
\end{figure}

@@

In this section, we give an overview of the dynamics of CHILDREN's two flagship programs. We focus on the number of estimated ultimate beneficiaries in both programs, median total subsidy, median subsidy per institution, and median subsidy per beneficiary. We also look at selected outcomes, i.e. those related to health as well as self-worth and day-to-day skills. We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt). We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur). These are only available after logging in on DESTATIS. The organizations also gave information about their total yearly budget. We inflate this with the general price index.

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 18:39:45 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

Table \ref{fundamentalDynamics} shows that, at the beginning of the time series in 2011, in the Lunch program they supported in 52 organizations. In 2018, this number has increased to 68. In 2011, CHILDREN financed meals for 3748 beneficiaries, and for 5103 in 2018. In the trips program, which launched in 2012, the number of supported organizations amounted to 44 in 2012 and grew to 49 until 2018. In 2012, their grant allowed 2803 beneficiaries to go on trips, and 6911 in 2018.

@@

\floatfoot{This graph shows the development of grants in the Meals compared to the Trips program. We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary. From left to right: Meals, Trips. From top to bottom: sum, median, median per beneficiary. We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
\end{figure}

For the dynamics of figure \ref{totalGrantsDyn} we visualze the dynamics of CHILDRENs' grants by distinguishing between the sum of grants in one year, the median and the median grant per beneficiary. We also compare the grants of the Lunch and the Trips Program.

Figure \ref{totalGrantsDyn} shows no exact trend for the total real grant for the Lunch program. Between 2013 and 2015 the grant increased from about 600000 EUR to 680000 EUR, but falls behind in the following year. Since 2017 an increase is again visible. In comparison to this, there is a clearer negative trend in median Meals subsidy, falling from about 8000 EUR in 2012 to about 6500 EUR in 2018. In accordance, the median Meals grant per beneficiary shrinks from about 250 EUR to about 200 EUR.

In the total Trips grant, a slightly negative trend is visible, after the subsidy increased to approximately 200000 EUR in 2014, but decreased to about 130000 EUR in 2016, and is connstand eversince. The Trips median grant therefore also decreased from 3000 EUR to 2000 EUR over the time period, as well as the median grant per beneficiary decreased from about 60 EUR to about 30 EUR.

These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table \ref{fundamentalDynamics}, that children was able to increase the number of organizations they support, but had to distribute the available subsidy among them.

@@

In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the degree to which beneficiaries: are healthier, have a growing appreciation for a healthier diet, and have increased their knowledge about what constitutes a healthy diet. Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For this figure, we use the original ordinal varibles which result from the survey structure.

@@

\begin{equation}
\label{SimpleLinearModel}
  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
\end{equation}

In this section we use a simple linear model with, as described in equation \ref{SimpleLinear Model}. We look at the association between:

\begin{itemize}
  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Meals program and the number of meals it dispenses}
  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Trips program and the number of trips it conducts}
  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' self-worth}
  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' everyday expertise}
   \item{a standardized measure of the healthiness of the meals an organization dispenses and various standardized health-related outcomes of beneficiaries} 
\end{itemize}

We discuss all these models in turn.

\subsection{Direct effects of CHILDREN's grants}

If CHILDREN's grants are to have an effect on beneficiaries, they should first influence the output of organizations in terms of meals dispensed and trips conducted.

As table \ref{GrantsRegressionsLunch} shows, this is emphatically true. Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident. 
The estimated coefficents are very similar when we use the original dataset and the one with imputed values. In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed. This estimate is highly statistically significant. When we exclude outliers, i.e. those organizations that give out very many menus or very few menus,
the estimated coefficent decreases by about one order of magnitude. Still, spending not much more than three EUR more goes hand in hand with one extra meal. The estimate is also highly statistically significant.

\usepackage{booktabs}

\begin{table}
\caption{Regression Results: Number of meals}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\toprule
 & OLS & OLS without Outliers & OLS Impute \\
\midrule
(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
\midrule
R$^2$       & 0.43            & 0.13            & 0.45             \\
Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
Num. obs.   & 329             & 250             & 440              \\
RMSE        & 39992.79        & 3629.72         & 39601.41         \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\ $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{GrantsRegressionsLunch}
\end{center}
\end{table}

In the remit of the Trips program, the picture looks much different.

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept)      & $3.7049^{***}$ & $2.6236^{***}$ & $3.6237^{***}$ \\
                 & $(0.3313)$     & $(0.2300)$     & $(0.3253)$     \\
realTripsSubsidy & $0.0002^{*}$   & $0.0003^{***}$ & $0.0002^{*}$   \\
                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
\hline
R$^2$            & 0.0474         & 0.0880         & 0.0504         \\
Adj. R$^2$       & 0.0444         & 0.0844         & 0.0476         \\
Num. obs.        & 322            & 257            & 334            \\
RMSE             & 2.9565         & 1.6981         & 2.9310         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of trips}
\label{GrantsRegressionsTrips}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
\hline
R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
Num. obs.           & 121          & 120         & 177          & 177          \\
RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Less Ill}
\label{HealthRegressions-LessIll}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
\hline
R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
Num. obs.           & 214      & 212      & 275        & 275      \\
RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Dietary Knowledge}
\label{HealthRegressions-DietaryKnowledge}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
\hline
R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
Num. obs.           & 213          & 211      & 274          & 274        \\
RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Appreciate Healthy}
\label{HealthRegressions-AppreciateHealthy}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
Num. obs.                      & 428      & 184      & 430      & 187      \\
RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Selfworth}
\label{SelfworthRegressions}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
Num. obs.                      & 426      & 177      & 429      & 181      \\
RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: dayToDaySkills}
\label{DayToDaySkillsRegressions}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 18:39:51
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

As an option to run an regression on the original ordinal variables, we use the vglm function from the VGAM package...

Use from zwichenpräsentation

\begin{equation}
\label{ModelProdu}
\ln y_{it} = \frac{}{}  \sum
\end{equation}
